Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-18 Docs/TODAES/paper.tex
including first version of TODAES template

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes
\usepackage{cite}

\usepackage{hyphenat}
\usepackage[english]{babel}
\hyphenation{ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

\newcommand{\head}[1]{\textnormal{\textbf{#1}}}
\renewcommand{\lstlistingname}{Algorithm}
\renewcommand{\arraystretch}{1.3}
\usepackage[table]{xcolor}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{Gray}{gray}{0.93}
\definecolor{DarkGray}{gray}{0.70}

\lstset{frame=tb,
  language=c,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{black},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

\renewcommand{\baselinestretch}{0.96}

\newcommand{\comment}[1]{}

\begin{document}
\title{Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning}
\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Helder Silva \and Lucas Cordeiro}

\institute{A. Trindade, H. Ismail, R. Degelo, E. Galv\~ao \at
              Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
%              Tel.: +123-45-678910\\
%              Fax: +123-45-678910\\
              \email{\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com}          %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           H. Silva and L. Cordeiro \at
              Federal University of Amazonas, Brazil
              \email: prhsilva2012@gmail.com lucascordeiro@ufam.edu.br           %  \\
}

@@

\keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }

@@

\comment{In any HW and SW design of complex systems, more time is spent on verification than on construction~\cite{Baier2008}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Software (and systems) may be viewed as mathematical objects with behavior that is, in principle, well determined. This makes it possible to specify software using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the software meets its specification ~\cite{Clarke2009}. Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors. Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner. The system models are accompanied by algorithms that systematically explore all the states of the system model.}

@@

\comment{Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}. In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}. However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.}

@@

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}. 
\comment{In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages. The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit. Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.}
There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints
\begin{equation}
\label{linear-programming-problem}
  minf^t x \: such \; that  = 
  \begin{cases}
    A.x \leq b, \\ 
    Aeq.x = beq, \\ 
    x \geq 0.
  \end{cases}
\end{equation}

@@

\comment{
Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior~\cite{Baier2008}, ~\cite{Clarke2009}. These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry. However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components ~\cite{Biere2009}. Much research has been devoted to mitigate this problem.
}

@@

In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems~\cite{Cordeiro2012}. 
\comment{According to Cordeiro {\it et al.}~\cite{Cordeiro2012},\cite{Cordeiro2011}, SMT-based model checking can be used to verify single- and multi-threaded software in embedded systems. In Ramalho {\it et al.}~\cite{Ramalho2013}, ESBMC can also be used to model check C$++$ software based on SMT solvers. In Trindade {\it et al.}~\cite{Trindade2015},\cite{Trindade2016}, it was shown that it is possible to use ESBMC also as an optimization tool.}
In particular, there are two directives in ESBMC that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT. The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition (minimum hardware cost). Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.

@@

Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}. In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style. GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver. The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver). Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}. Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
	\caption{ESBMC Architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

\comment{SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.}

@@

Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.
%
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

\comment{
%----------------------------------------------
\section{Partitioning problem using ILP-based,Genetic Algorithms}
\label{ILPGA}
%----------------------------------------------

The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2016}. Both use slack variables in order to be possible to represent constraints and to use commercial tools. However, GA had improvements from the parameters of related studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of generations changed from $100*NumberOfVariables$ (default) to $75$.
}

@@

To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
	\caption{ESBMC-SS Approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
	\caption{ESBMC-PS Approach. }
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

The most optimized approach applies a parallelized binary search to reduce the amount of steps to be executed in order to find the optimal solution. A controller is designed to return the step to be executed so that the number of verification runs are substantially reduced. The parallelized binary search accomplishes this by splitting the domain of possible values into intervals and then by returning the middle of the largest interval so that two new intervals are created.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
	\caption{ESBMC-PB Approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$. When the next available core asks for a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$). The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.
%
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
	\caption{Binary Step Calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

\begin{table}[h]
\caption {Description of Benchmarks.}
\small
\sffamily\footnotesize
\tabulinesep=6pt
\begin{tabular}[c]{m{1.5cm}m{0.8cm}m{0.8cm}m{3.8cm}}
  \toprule[1.5pt]
  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
  \midrule

@@

\begin{thebibliography}{5}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi
\providecommand{\eprint}[2][]{\url{#2}}

%1
\bibitem{Arato2003}
Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D. (2003), ``{Hardware/software partitioning in embedded system design},'' In: Proc. of the Intl. Symp. of Intelligent Signal Processing, pp. 192--202.

%2
\bibitem{Mann2007}
Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System Design, v. 31, n. 3 pp. 241--263.

%3
\bibitem{Trindade2015}
Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).

%4
\bibitem{Trindade2016}
Trindade, A. B., Ismail, H. I., Cordeiro, L. C. (2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1-4.

%5
\bibitem{Bjorner2015}
Bjorner, N., Phan, A-D., Fleckenstein, L. (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 194--199.

%6
\bibitem{Tang2009}
Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.

%7
\bibitem{OpenMP1998}
OpenMP Architecture Review Board, OpenMP C and C++
Application Pogram Interface, Version 1.0, October 1998.
http://www.openmp.org

%8
\bibitem{Cordeiro2012}
Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.

%9
\bibitem{Rao2009}
Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.

%10
\bibitem{Biere2009}
Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.

>>>>

% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes
\usepackage{cite}
\usepackage{hyphenat}
\usepackage[english]{babel}

\hyphenation{ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}

% Copyright
\setcopyright{rightsretained}

% DOI
\doi{0000001.0000001}

%ISSN
\issn{1234-56789}

% Document starts
\begin{document}

% Page heads
\markboth{G. Zhou et al.}{A Multifrequency MAC Specially Designed for WSN Applications}

\title{Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning}

% Title portion
\author{
Alessandro Trindade
\affil{Federal University of Amazonas}
Hussama Ismail
\affil{Federal University of Amazonas}
Edilson Galv\~ao\
\affil{Federal University of Amazonas}
Helder Silva
\affil{Federal University of Amazonas}
Lucas Cordeiro\affil{Federal University of Amazonas}
}

% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010575.10010755</concept_id>
%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010553.10010554</concept_id>
%  <concept_desc>Computer systems organization~Robotics</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>10003033.10003083.10003095</concept_id>
%  <concept_desc>Networks~Network reliability</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>  
%\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

%\terms{Design, Algorithms, Performance}

\keywords{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP. }

%\acmformat{Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic,
%and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially
%designed for  wireless sensor network applications.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

\begin{bottomstuff}
A. Trindade, H. Ismail, R. Degelo, E. Galv\~ao \\
Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com \\ \\
\and\\ \\
H. Silva and L. Cordeiro \\
Federal University of Amazonas, Brazil\\
prhsilva2012@gmail.com lucascordeiro@ufam.edu.br      \\
\end{bottomstuff}

@@

@@

%In any HW and SW design of complex systems, more time is spent on verification than on construction~\cite{Baier2008}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Software (and systems) may be viewed as mathematical objects with behavior that is, in principle, well determined. This makes it possible to specify software using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the software meets its specification ~\cite{Clarke2009}. Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors. Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner. The system models are accompanied by algorithms that systematically explore all the states of the system model.

@@

%Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}. In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}. However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.

@@

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}.

%In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages. The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit. Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.

There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints
\begin{equation}
\label{linear-programming-problem}
  minf^t x \: such \; that  = 
  \begin{cases}
    A.x \leq b, \\ 
    Aeq.x = beq, \\ 
    x \geq 0.
  \end{cases}
\end{equation}

@@

%Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior~\cite{Baier2008}, ~\cite{Clarke2009}. These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry. However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components ~\cite{Biere2009}. Much research has been devoted to mitigate this problem.

@@

In this study, ESBMC has been used as a BMC tool to solve HW-SW partitioning problems~\cite{Cordeiro2012}. 
%According to Cordeiro {\it et al.}~\cite{Cordeiro2012},\cite{Cordeiro2011}, SMT-based model checking can be used to verify single- and multi-threaded software in embedded systems. In Ramalho {\it et al.}~\cite{Ramalho2013}, ESBMC can also be used to model check C$++$ software based on SMT solvers. In Trindade {\it et al.}~\cite{Trindade2015},\cite{Trindade2016}, it was shown that it is possible to use ESBMC also as an optimization tool.}
In particular, there are two directives in ESBMC that can be used to guide a model checker to solve an optimization problem: ASSUME and ASSERT. The directive ASSUME is responsible for ensuring the compliance of constraints (software costs), and the directive ASSERT controls the halt condition (minimum hardware cost). Then, with some C/C++ code, it is possible to guide ESBMC to solve optimization problems.

@@

Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}. In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style. GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver. The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver). Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}. Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
	\caption{ESBMC Architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

%SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.

@@

Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.
%
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=95px]{figures/vzArch.png} 
	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

%\comment{
%----------------------------------------------
%\section{Partitioning problem using ILP-based,Genetic Algorithms}
%\label{ILPGA}
%----------------------------------------------

%The ILP and GA were taken from our previous studies~\cite{Trindade2015,Trindade2016}. Both use slack variables in order to be %possible to represent constraints and to use commercial tools. However, GA had improvements from the parameters of related %studies in order to increase the solution accuracy without producing timeout. The tuning was performed by empirical tests and %resulted in changing of three parameters, which are passed to the function \textit{ga} of MATLAB~\cite{TheMathWorks2013}: the %population size was set from $300$ to $500$, the Elite count changed from $2$ (default value) to $50$, and the number of %generations changed from $100*NumberOfVariables$ (default) to $75$.
%}

@@

To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{figures/esbmc-parallel.pdf} 
	\caption{ESBMC-SS Approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{figures/esbmc-parallel.png} 
	\caption{ESBMC-PS Approach. }
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

The most optimized approach applies a parallelized binary search to reduce the amount of steps to be executed in order to find the optimal solution. A controller is designed to return the step to be executed so that the number of verification runs are substantially reduced. The parallelized binary search accomplishes this by splitting the domain of possible values into intervals and then by returning the middle of the largest interval so that two new intervals are created.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{figures/esbmc-parallel-Controler.png} 
	\caption{ESBMC-PB Approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$. When the next available core asks for a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$). The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.
%
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=75px]{figures/Fig4.png}
	\caption{Binary Step Calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

\begin{table}[h]
\caption {Description of Benchmarks.}
\small
\sffamily\footnotesize
\tabulinesep=6pt
\begin{tabular}[c]{m{1.5cm}m{0.8cm}m{0.8cm}m{3.8cm}}
  \toprule[1.5pt]
%  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
  \midrule

@@

% Bibliography
%\bibliographystyle{ACM-Reference-Format-Journals}
%\providecommand{\natexlab}[1]{#1}
%\providecommand{\url}[1]{{#1}}
%\providecommand{\urlprefix}{URL }
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi
%\providecommand{\eprint}[2][]{\url{#2}}

%1
%\bibitem{Arato2003}
%Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D. (2003), ``{Hardware/software partitioning in embedded system %design},'' In: Proc. of the Intl. Symp. of Intelligent Signal Processing, pp. 192--202.

%2
%\bibitem{Mann2007}
%Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System %Design, v. 31, n. 3 pp. 241--263.

%3
%\bibitem{Trindade2015}
%Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded %systems,}'' In: Design Automation for Embedded Systems (to appear).

%4
%\bibitem{Trindade2016}
%Trindade, A. B., Ismail, H. I., Cordeiro, L. C. (2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in %Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1-4.

%5
%\bibitem{Bjorner2015}
%Bjorner, N., Phan, A-D., Fleckenstein, L. (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc. of the Intl. Conf. on %Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 194--199.

%6
%\bibitem{Tang2009}
%Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. %on Computer Science Education},'' pp. 1900--1905.

%7
%\bibitem{OpenMP1998}
%OpenMP Architecture Review Board, OpenMP C and C++
%Application Pogram Interface, Version 1.0, October 1998.
%http://www.openmp.org%

%8
%\bibitem{Cordeiro2012}
%Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: %IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.

%9
%\bibitem{Rao2009}
%Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.

%10
%\bibitem{Biere2009}
%Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of %Satisfiability, IOS Press, pp. 457–-481.
